---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![img](https://img.shields.io/badge/Lifecycle-Experimental-339999)](https://github.com/bcgov/repomountie/blob/master/doc/lifecycle-badges.md)

# bcstatslinks

This package contains a shiny module to be incorporated into bcstats shinyapps, 
to provide a drop down menu with links to other BCStats shinyapps. 

This repo also houses the csv file used to feed this drop down list, see inst/extdata/bcstats_links.csv. This csv must remain in this location with the two columns: name and url, but should be updated with new rows as new apps are created.

### Installation

TBD

#### Example

This is a basic example which shows you how to incorporate the drop down list in your shiny app:

```{r example}
ui <- shiny::fluidPage(
  linkModUI(id = 'linkModule')
  )

server <- function(input, output) { 
  linkModServer(id = 'linkModule')
  }

shiny::shinyApp(ui = ui, server = server)
```

### Project Status

Experimental

### Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov/bcstatslinks/issues/).

### How to Contribute

If you would like to contribute to the package, please see our 
[CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

### License

```
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the &quot;License&quot;);
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an &quot;AS IS&quot; BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
```

---
*This project was created using the [bcgovr](https://github.com/bcgov/bcgovr) package.* 
